### 2021-04-29 sections/queueing_model/main.tex
Update known.py
Create subsections/ subdirectory
Minor edits on figures
Reference figure of previous section and change the caption of
the general Markov chain figure

\section{A queueing models with 2 consecutive buffer centres}

@@

The model consists of two types of individuals; class 1 and class 2.
Class 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
receive their service. 
Class 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed to the next waiting zone only when the number of 
individuals in the next system (in waiting zone 1 and in service) is less than a 
pre-determined threshold \(T\).
When the threshold is reached, all class 2 individuals that arrive will remain 
\textit{``blocked''} in the buffer centre until the number of people in the 
system is reduced below \(T\).

% TODO: Possibly worth including the diagram of the queueing model here

@@

% \input{sections/queueing_model/general-markov-model/main.tex}

@@

\subsection{Performance Measures}

\subsection{Example}

>>>>

\section{A queueing model with 2 consecutive buffer centres}

@@

The model consists of two types of individuals; class 1 and class 2.
Class 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
receive their service. 
Class 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed to the next waiting zone only when the number of 
individuals in the next system (in waiting zone 1 and in service) is less than a 
pre-determined threshold \(T\).
When the threshold is reached, all class 2 individuals that arrive will remain 
\textit{``blocked''} in the buffer centre until the number of people in the 
system is reduced below \(T\). 
This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.

@@

\input{sections/queueing_model/general-markov-model/main.tex}

@@

\input{sections/queueing_model/subsections/performance_measures/main.tex}

\input{sections/queueing_model/subsections/example/main.tex}
